\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-02 slides/gvn-hoist.tex
clean up

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item compute value number of scalars, loads, stores, calls
  \item compute insertion points of each type of instructions
  \item hoist expressions
  \item propagate changes by upating SSA
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  \begin{itemize}
  \item loads: value number the pointer operand
  \item stores: value number the pointer operand and the value being stored
  \item calls, Scalars: use the existing GVN infrastructure
  \end{itemize}
}

@@

  \begin{itemize}
  \item Compute a common insertion point for a set of instructions having the same GVN.
    (Similar to VBEs but not as strict)
  \item Partition the candidates into a smaller set of hoistable candidates when
    no common insertion points can be found (The instructions are sorted by their DFS numbers)
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-hoist expressions}
  \begin{itemize}
  \item Scalars: Just move one of the instructions to the hoisting point and remove others. Update SSA.
  \item Loads and Stores: Try to make geps available (if not), and then hoist. Update SSA and memory SSA.
  \item Calls: Hoist just like scalars. Update SSA.
  \item Set minimum alignment among all the candidates for loads and stores, maximum for allocas.
  \end{itemize}
}

@@

\frame{\frametitle{Cost models}
  \begin{itemize}
  \item Limit the number of Basic Blocks in the path between initial position
    and the hoisting point
  \item Limit the number of instructions between the initial position and the
    beginning of its Basic Block
  \item Do not hoist GEPs
  \item Limit the number of dependent instructions to be hoisted
  \end{itemize}
}

>>>>

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item compute value number of scalars, loads, stores, calls
  \item compute insertion points of each type of instructions
  \item hoist expressions
  \item propagate changes by updating SSA
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  current GVN not accurate for loads and stores:
  \begin{itemize}
  \item scalars: use the existing GVN infrastructure
  \item loads: VN the pointer operand
  \item stores: VN the pointer operand and the value being stored
  \item calls: as stores, loads, or scalars (following side effects)
  \end{itemize}
}

@@

  \begin{itemize}
  \item Compute a common insertion point for a set of instructions having the same GVN
    (Similar to VBEs but not as strict)
  \item Partition the candidates into a smaller set of hoistable candidates when
    no common insertion points can be found
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-hoist expressions}
  \begin{itemize}
  \item scalars: just move one of the instructions to the hoisting point and remove others; update SSA
  \item loads and stores: try to make geps available, then hoist; update SSA and memory SSA
  \end{itemize}
}

@@

\frame{\frametitle{Cost models}
  \begin{itemize}
  \item limit the number of basic blocks in the path between initial position
    and the hoisting point
  \item limit the number of instructions between the initial position and the
    beginning of its basic block
  \item do not hoist GEPs
  \item limit the number of dependent instructions to be hoisted
  \end{itemize}
}
